---
title: "3770 HW6"
author: "Darnell Chen"
date: "2024-10-23"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 6.1.6

The sample mean of our data set can be calculated by adding all our values and dividing by the sample size:\\

$\bar{x} = \sum_{i=1}^n x_i \approx 14.35895$

On the other hand, our standard deviance is simply the squareroot of our variance $s^2$:

$s^2 = \frac{\sum_{i=1}^n (x_i - \mu)^2}{n-1} \approx 356.4716$\
$s = \sqrt{s^2} = \sqrt{356.4716} \approx 18.88045$

Thus, we get a mean of approx. 14.35895 and a standard deviation of approx. 18.88045.

```{r}
times = read.table("6-8.txt", header = TRUE)
times = times$time

mean(times)

var(times)
sqrt(var(times))
```

$~$

\pagebreak

## Problem 6.2.4

The two middle numbers in our data set are both 90.4. Since $\frac{90.4 + 90.4}{2} = 90.4$, our median is thus, 90.4.

```{r}
rating = read.table("6-30.txt", header = TRUE)
rating = rating$Rating

median(rating)
```

Our Quartiles:

```{r}
quantiles = quantile(rating,type=6)
quantiles
```

Our Stem and Leaf Plot:

```{r}
stem(rating, scale = 2)
```

```{=tex}
\begin{table}[h!]
\centering
\begin{tabular}{|c|l|c|}
\hline
\textbf{Value} & \textbf{Digits}       & \textbf{Frequency} \\ \hline
83  & 4             & 1  \\ \hline
84  & 33            & 2  \\ \hline
85  & 3             & 1  \\ \hline
86  & 777           & 3  \\ \hline
87  & 456789        & 6  \\ \hline
88  & 23334556679   & 11 \\ \hline
89  & 0233678899    & 10 \\ \hline
90  & 0111344456789 & 13 \\ \hline
91  & 0001112256688 & 13 \\ \hline
92  & 22236777      & 8  \\ \hline
93  & 023347        & 6  \\ \hline
94  & 2247          & 4  \\ \hline
95  &               & 0  \\ \hline
96  & 15            & 2  \\ \hline
97  &               & 0  \\ \hline
98  & 8             & 1  \\ \hline
99  &               & 0  \\ \hline
100 & 3             & 1  \\ \hline
\end{tabular}
\end{table}
```

\pagebreak

<<<<<<< HEAD
=======
$~$

$~$

$~$

$~$

$~$

$~$

$~$

$~$

$~$

$~$

$~$

$~$

$~$

$~$

$~$

$~$

$~$

$~$

$~$

$~$



>>>>>>> 5b4146ed09155bdef06b4ece52c098b7217fb2f9
## Problem 6.3.2

Our Histogram:

```{r}
bin=seq(min(rating),max(rating),by=(max(rating)-min(rating))/8)
freqs = hist(rating, breaks=bin, label=TRUE, right=FALSE, col=rainbow(8), ylim=c(0, 32))
freqs
```

Our Frequency Table:

```{r}
str=NULL
for (i in 1:7) {
str = c(str, paste(freqs$breaks[i], "$\\le x < $", freqs$breaks[i+1]))
}
# Handle the last interval with inclusive bounds
str = c(str, paste(freqs$breaks[8], "$\\le x \\le $", freqs$breaks[9]))
<<<<<<< HEAD
df = data.frame(Class=str, Index=freqs$counts)
library(knitr)
library(kableExtra)
kable(df, "latex", align="c", escape = F, caption="Hint") %>%
  kable_styling(latex_options = "hold_position")
=======

relative_freq = freqs$counts / sum(freqs$counts)
cum_freq = cumsum(relative_freq)

df = data.frame(Class=str, Index=freqs$counts, 
                "Relative Frequency"=relative_freq, "Cumulative Frequency"=cum_freq)
library(knitr)
library(kableExtra)
kable(df, "latex", align="c", escape = F, caption="Frequency Table") %>%
kable_styling(latex_options = "hold_position")
>>>>>>> 5b4146ed09155bdef06b4ece52c098b7217fb2f9
```

$~$

\pagebreak

## Problem 6.4.9

Based on my boxplot below, I think it's hard to definitively tell if the treatment is effective or not in gene expression. Because while it does have the smallest range - and practically no outliers - there's still a ton of difference in variance between the control groups. However, the variance and outliers in the High Dosage group itself definitely displayed a much smaller range compared to the other groups. So if I had to choose a definitive answer, I'd say that the high dosage treatment definitely helped in minimizing gene expression.

```{r}
treatmentData = read.table("6-81.txt", header=TRUE)
attach(treatmentData)
boxplot(Expression~Group, col=rainbow(10))
```

$~$

\pagebreak

## Problem 6.7.2

Based on the normal distribution line below, it would be reasonable to assume that the octane rating follows a normal distribution. This is because most of our ratings/points follow the expected normal distribution line.

```{r}
qqnorm(rating)
qqline(rating, col="red")
```
