---
title: "3770 HW6"
author: "Darnell Chen"
date: "2024-10-23"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 6.1.6

The sample mean of our data set can be calculated by adding all our values and dividing by the sample size:\\

$\bar{x} = \sum_{i=1}^n x_i \approx 14.35895$

On the other hand, our standard deviance is simply the squareroot of our variance $s^2$:

$s^2 = \frac{\sum_{i=1}^n (x_i - \mu)^2}{n-1} \approx 356.4716$\
$s = \sqrt{s^2} = \sqrt{356.4716} \approx 18.88045$

Thus, we get a mean of approx. 14.35895 and a standard deviation of approx. 18.88045.

```{r}
times = read.table("6-8.txt", header = TRUE)
times = times$time

mean(times)

var(times)
sqrt(var(times))
```

$~$

\pagebreak
## Problem 6.2.4

The two middle numbers in our data set are both 90.4. Since $\frac{90.4 + 90.4}{2} = 90.4$, our median is thus, 90.4.

```{r}
rating = read.table("6-30.txt", header = TRUE)
rating = rating$Rating

median(rating)
```

Our Quartiles:
```{r}
quantiles = quantile(rating,type=6)
quantiles
```
Our Stem and Leaf Plot:
```{r}
stem(rating, scale = 2)
```

$~$

\pagebreak
## Problem 6.3.2

Our Histogram:

```{r}
bin=seq(min(rating),max(rating),by=(max(rating)-min(rating))/8)
freqs = hist(rating, breaks=bin, label=TRUE, right=FALSE, col=rainbow(8), ylim=c(0, 32))
freqs
```

Our Frequency Table:
```{r}
str=NULL
for (i in 1:7) {
  str = c(str, paste(freqs$breaks[i], "$\\le x < $", freqs$breaks[i+1]))
}

# Handle the last interval with inclusive bounds
str = c(str, paste(freqs$breaks[8], "$\\le x \\le $", freqs$breaks[9]))

df = data.frame(Class=str, Index=freqs$counts)
library(knitr)
library(kableExtra)
kable(df, "latex", align="c", escape = F, caption="Hint") %>%
kable_styling(latex_options = "hold_position")
```

$~$

\pagebreak
## Problem 6.4.9

Based on my boxplot below, I think it's hard to definitively tell if the treatment is effective or not in gene expression. Because while it does have the smallest range - and practically no outliers - there's still a ton of difference in variance between the control groups. However, the variance and outliers in the High Dosage group itself definitely displayed a much smaller range compared to the other groups. So if I had to choose a definitive answer, I'd say that the high dosage treatment definitely helped in minimizing gene expression.
```{r}
treatmentData = read.table("6-81.txt", header=TRUE)
attach(treatmentData)
boxplot(Expression~Group, col=rainbow(10))
```
$~$

\pagebreak
## Problem 6.7.2

Based on the normal distribution line below, it would be reasonable to assume that the octane rating follows a normal distribution. This is because most of our ratings/points follow the expected normal distribution line.

```{r}
qqnorm(rating)
qqline(rating, col="red")
```
