---
title: "Homework 1 - ISYE 3770"
author: Darnell Chen
output: pdf_document
date: "2024-08-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# PART 1 - Textbook Questions

## Q2.1.13

**a)** 3 + 5 + 6 + 8\
**b)** 1 + 2\
**c)** 1 + 2 + 3 + 4 + 5\
**d)** 7 + 8\
**e)** 3 + 4 + 5\

## Q2.1.21

**a)** $A' = \{ x \mid x \geq 72.5 \}$

**b)** $B' = \{ x \mid 0 < x \leq 52.5 \}$

**c)** $A \cap B = \{ x \mid 52.5 < x < 72.5 \}$

**d)** $A \cup B = \{ x \mid x > 0 \}$

*Note*: Sample space is positive real numbers.

## Q2.2.13

<!-- $\frac{5!}{4!}\cdot\frac{45!}{6!39!} + \frac{5!}{5!}\cdot\frac{45!}{5!40!}$\ -->

$C_4^5\times C_6^{45} + C_5^5\times C_5^{45}$

```{r}
choose(5, 4) * choose(45, 5) + choose(5, 5) * choose(45, 5)
```

## Q2.3.1

**a)** $P(A) = 0.1 + 0.1 + 0.2 = 0.4$\
**b)** $P(B) = 0.2 + 0.4 + 0.2 = 0.8$\
**c)** $P(A^\prime) = 0.4 + 0.2 = 0.6$\
**d)** $P(A\cup B) = 0.1 + 0.1 + 0.2 + 0.4 + 0.2 = 1$\
**e)** $P(A\cap B) = 0.2$\

## Q2.3.17

**a)** $A = \frac{52^8}{62^8}$\
**b)** $B = \frac{10^8}{62^8}$\
**c)** $62^8 - 52^8$\
**d)** $\frac{10!}{2!}\cdot 52^6$\

**a)** $A = \frac{52^8}{62^8}$\
**b)** $B = \frac{10^8}{62^8}$\
**c)** $62^8 - 52^8$\
**d)** $10^2\cdot 52^6$\

## Q2.4.7

**a)** $\frac{C_1^5 \times 36^5}{36^6}$

```{r}
choose(5, 1) * (36**5) / 36**6
```

**b)** $\frac{36^5 \times C_1^5}{36^6}$

```{r}
(36**5) * choose(5, 1) / 36**6
```

**c)** $\frac{C_1^5 \times 36^4 \times C_1^5}{36^6}$

```{r}
choose(5, 1) * (36**4) * choose(5, 1) / 36**6
```

**d)** $\frac{2 \times C_1^5 \times 36^5 -  C_1^5 \times 36^4 \times C_1^5}{36^6}$\

```{r}
(2 * choose(5, 1) * 36**5 - choose(5, 1) * 36**4 * choose(5, 1)) / 36**6
```

# PART 2

## Find the numbers of combinations for the following 5-card Poker hand.

**a)** Three of a Kind It contains three cards of the same number(rank), plus two cards which are not of this number nor the same as each other. For example: AAA83, KKK72, . . .

*Solution:* $C_1^{13} \times C_3^4 \times C_1^{48} \times C_1^{47}$

```{r}
choose(13, 1) * choose(4, 3) * choose(48, 1) * choose(47, 1)
```

# PART 3

## Four Candidates: A, B, C, and D run for the president of GT Elementary School. Suppose we have 100 voters (students) and everyone needs to vote for exactly one candidate from A, B, C, and D and the votes are anonymous. How many different voting results (combinations) can we have here? [5 pts]

*Solution:* $C_4^{100+4-1}$

```{r}
choose(100+4-1, 4)
```
