---
title: "Homework 2"
author: "Darnell Chen"
date: "2024-09-08"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Q2.5.4

**a)** $P(gas~leak~ | ~failures) = \frac{87}{107}$

```{r}
87/107
```

**b)** $P(electrical~fail~ | ~gas~leak) = \frac{32}{87}$

```{r}
32/87
```

**c)** $P(gas~leak~|~electrical~fail) = \frac{55}{72}$

```{r}
55/72
```

$~$

## Q2.5.6

**a)** $P(second~defective~|~first~is~defective) = \frac{4}{499} \approx 0.008016032$

```{r}
(4/499)
```

**b)** $P(defective) \cdot P(second~defective~|~first~is~defective) = \frac{5}{500} \cdot \frac{4}{499} \approx 0.00008016032$

```{r}
(5/500) * (4/499)
```

**c)** $P(acceptable) \cdot P(second~acceptable~|~first~is~acceptable) = \frac{495}{500} \cdot \frac{494}{499} \approx 0.9800802$

```{r}
(495/500) * (494/499)
```

\newpage

**Extra)**\
P(A) = probability first card is defective = 5/500\
P(A') = probability first card isn't defective = 495/500\
P(B\|A) = probability second card is defective given first card is defective = 4/499\
P(B\|A') = probability second card is defective given first card isn't defective = 5/499\
P(B) = probability second card is defective\
$$
\begin{aligned}
P(B) &= P(B|A)P(A) + P(B|A')P(A')\\
&= \frac{4}{499} \cdot \frac{5}{500} + \frac{5}{499} \cdot \frac{495}{500}\\
&= \frac{20}{499\cdot 500} + \frac{2475}{499*500}\\
&= \frac{2495}{499*500}\\
&= 0.01
\end{aligned}
$$

```{r}
(5*495)/(499*500) + 20/(499*500)
```

$~$

## Q2.6.3

$0.9 \cdot P(failure~|~dry) + 0.1(failure~|~wet) = 0.9\cdot 0.01 + 0.1\cdot 0.05 = 0.014$

```{r}
0.9*0.01 + 0.1*0.05
```

$~$

## Q2-141

**a)** First we calculate P(B'):\
$$
\begin{aligned}
P(B') &= P(\Omega ) - P(B)\\
&= 1 - \frac{10^8}{62^8}
\end{aligned}
$$

Then we can calculate P(A\|B'):\

$$
\begin{aligned}
P(A|B') &= \frac{P(A \cap B')}{P(B')}\\
&= \frac{P(A)}{P(B')}\\
&= \frac{\frac{52^8}{62^8}}{1 - \frac{10^8}{62^8}}\\
&\approx {0.2448462}
\end{aligned}
$$

```{r}
(52**8/62**8) / (1-(10**8/62**8))
```

$~$

**b)** We know that B is a subset of A$^\prime$ since A$^\prime$ is simply all combinations that contains at least 1 letter. Therefore $B = A^\prime \cap B$\
Then we simply calculate P(B):\

$$
\begin{aligned}
  P(B) &= \frac{|B|}{|\Omega |}\\
  &= \frac{10^8}{62^8}\\
  &\approx 4.580011e-07
\end{aligned}
$$

```{r}
(10**8) / (62**8)
```

$~$

**c)**\
$$
\begin{aligned}
  P(contains~exactly~2~int~|~contains~at~least~1~int) &= \frac{P(contains~exactly~2~int~ \cap ~contains~at~least~1~int)}{P(contains~at~least~1~int)}\\
  &=\frac{P(contains~exactly~2~int)}{P(contains~at~least~1~int)}\\
  &= \frac{\frac{10^2 \cdot C_2^8\cdot 52^6}{62^8}}{1 - P(A)}\\
  &= \frac{\frac{10^2 \cdot C_2^8\cdot 52^6}{62^8}}{1 - \frac{52^8}{62^8}}\\
  &= \frac{10^2 \cdot \frac{8!}{2!6!}\cdot 52^6}{62^8 - 52^8}\\
  &\approx 0.3357447
\end{aligned}
$$

```{r}
((10**2)*(factorial(8)/(factorial(2)*factorial(6)))*(52**6))/(62**8 - 52**8)
```

## Problem 2.7.4

If P(A) $\neq$ P(A\|B) then we can say that the two aren't independent:

$$
\begin{aligned}
  P(A) = \frac{86}{100}\\
\end{aligned}
$$

$$
\begin{aligned}
  P(A|B) &= \frac{P(A \cap B)}{P(B)}\\
  &= \frac{\frac{70}{100}}{\frac{79}{100}}\\
  &= \frac{70}{79}
\end{aligned}
$$ Since $\frac{86}{100} \neq \frac{70}{79}$, we know that the two events A and B are not independent.

$~$

## Problem 2.8.9

**a)** $0.2 \cdot P(free~in~spam) + 0.8\cdot P(free~in~valid) = 0.2\cdot 0.6 + 0.8\cdot 0.04 = 0.152$

```{r}
0.2*0.6+0.8*0.04
```

**b)** 
$$
\begin{aligned}
P(is~spam~|~contains~free) &= \frac{P(is~spam~\cap ~contains~free)}{P(contains~free)} \\
&= \frac{P(~contains~free~|~is~spam ) \cdot P(is~spam)}{P(contains~free)} \\
&= \frac{0.6 \cdot 0.2}{0.152} \\
&\approx 0.7894737
\end{aligned}
$$

```{r}
0.6 * 0.2/0.152
```

**c)**

$$
\begin{aligned}
P(is~valid~|~not~contains~free) &= \frac{P(is~valid~ \cap ~not~contains~free)}{P(not~contains~free)} \\
&= \frac{P(not~contains~free~|~is~valid) \cdot P(is~valid)}{P(not~contains~free)} \\
&= \frac{0.96 \cdot 0.8}{1-0.152} \\
&\approx 0.1886792
\end{aligned}
$$

```{r}
(0.96-0.8) / (1-0.152)
```
