---
title: "Homework 3"
author: "Darnell Chen"
date: "2024-09-14"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 3.3.6

***a)***\
$P(X \leq 0) = f(0) = 0.17$\
$P(X \leq 2) = f(0) + f(2) = 0.17 + 0.35 = 0.52$\
$P(X \leq 3) = f(0) + f(2) + f(3) = 0.17 + 0.35 + 0.33 = 0.85$\
$P(X \leq 4) = f(0) + f(2) + f(3) + f(4) = 0.17 + 0.35 + 0.33 + 0.17 = 1$

$$ 
F(x) = 
\begin{cases} 
0 & \text{if } x < 0 \\
0.17 & \text{if } 0 \leq x < 2 \\
0.52 & \text{if } 2 \leq x < 3 \\
0.85 & \text{if } 3 \leq x < 3 \\
1 & \text{if } x \geq 2 
\end{cases} 
$$

***b)***\

$$
\begin{aligned}
Mean &= \sum_{x=0}^{4}x\cdot f(x)\\
&= 0(0.17) + 2(0.35) + 3(0.33) + 4(0.15)\\
&= 2.29
\end{aligned}
$$

```{r}
0*.17+2*.35+3*.33+4*.15
```

$$
\begin{aligned}
Variance &= [ \sum_{x}^4 x^2f(x)] - E[X]^2\\
&= 0^2(0.17) + 2^2(0.35) + 3^2(0.33) + 4^2(0.15) - 2.29^2\\
&= 1.5259
\end{aligned}
$$

```{r}
(0.17 * 0**2) + (0.35 * 2**2) + (0.33 * 3**2) + (0.15 * 4 ** 2) - (2.29 ** 2)
```

$~$

## 3.4.3

We first need to find the mean, variance, and standard deviation for $X$.\

$$
\begin{aligned}
mean ~of~ X = E[X] &= \sum_{x=0}^{9} x \cdot f(x)\\
&= \frac{a+b}{2}, where~a=upper~bound~and~b=lower~bound\\
&= \frac{9+0}{2}\\
&= 4.5
\end{aligned}
$$

$$
\begin{aligned}
variance~ of~ X = V[X] &= E[X^2] - (E[X])^2\\
&= \frac{(b - a + 1)^2-1}{12}\\
&= \frac{(9-0+1)^2-1}{12}\\
&= \frac{100}{12}\\
&= 8.25
\end{aligned}
$$

$$
\begin{aligned}
Standard~Deviation~of~X &= \sigma \\
&= \sqrt{\sigma^2}\\
&= \sqrt{8.25}\\
&\approx 2.872281
\end{aligned}
$$

```{r}
(9 + 0)/2
(((9 - 0 + 1)**2)-1)/12
sqrt(8.25)
```

Then using X, we can calculate the Mean, Variance, and Standard Deviation of $Y = 5X$:

Mean of Y = $E[5X]$ = $5E[X]$ = $5 \cdot 4.5$ = 22.5\
Variance of Y = $V[5X]$ = $25\cdot V[X]$ = $25 \cdot 8.25$ = 206.25\
Standard Dev. of Y = $\sqrt{\sigma^2}$ = $\sqrt{206.25}$ $\approx$ 14.36141

```{r}
5 * 4.5
25 * 8.25
sqrt(206.25)
```

$~$

## 3.5.13

***a)***\
$$
\begin{aligned}
P(X \leq 120) &= 1 - P(X \geq 121)\\
&= 1 - \sum_{x=121}^{125} \binom{125}{x}(0.9)^x(0.1)^{125-x}\\
&\approx 1 - 0.003858595\\
&\approx 0.9961414
\end{aligned}
$$

```{r}
pbinom(120, 125, 0.9)
```

***b)*** $P(X = 0) = \binom{125}{0}0.9^0(0.1)^{125} = 1 \times 10^{125}$

```{r}
dbinom(0, 125, 0.9)
```

$~$

## 3.6.6

***a)*** PMF = $f(x_i)$ = $(0.8)^{x_i}(0.2)$\
***b)*** f(2) = 1 - [P(X=0) + P(X=1)] = 1 - $[0.8\cdot 0.2 + 0.2]$ = 0.64\
***c)*** E[X] = $\frac{1}{p}$ = $\frac{1}{0.8}$ = 1.25\
***d)*** $$
\begin{aligned}
P(X \geq 3) &= 1-[P(X=0) + P(X=1)+P(X=2)]\\
&= 1 - [(0.8^00.2 + 0.8^10.2+0.8^20.2)]\\
&= 1 - 0.488\\
&= 0.512
\end{aligned}
$$

```{r}
1 - 0.8*0.2 - 0.2
1/0.8
1 - ((0.2*0.8**0)+(0.2*0.8**1)+(0.2*0.8**2))
```

$~$

## 3.6.13

***a)*** $P(X=2)$ = $\binom{10-1}{2-1} \cdot (0.8)^{8}(0.2)^2$ $\approx$ 0.06039798

***b)*** $P(X \leq 2)$ = $\binom{4-1}{2-1}$ $\cdot$ $(0.8)^{2}(0.2)^2$ + $\binom{3-1}{2-1}$ $\cdot (0.8)^{1}(0.2)^2$ + $\binom{2-1}{2-1}$ $(0.8)^0(0.2)^2$ = 0.1808

***C)*** $E[X=3]$ = $\frac{r}{p}$ = $\frac{3}{0.2}$ = 15

```{r}
dnbinom(8, 2, 0.2)

pnbinom(2, 2, 0.2)

3/0.2
```

$~$\

## 3.7.6

***a)*** P(X=6) = $\frac{\binom{6}{6} \binom{34}{0} }{\binom{40}{6}}$ $\approx$ $2.605266 \times 10^{-7}$

***b)*** P(X=5) = $\frac{\binom{6}{5} \binom{34}{1}}{\binom{40}{6}}$ $\approx$ $5.314742 \times 10^{-5}$

***c)*** P(X=4) = $\frac{\binom{6}{4} \binom{34}{2}}{\binom{40}{6}}$ $\approx$ 0.002192331

***d)*** $\frac{1}{P(X=6)}$ = $\frac{1}{\frac{\binom{6}{6} \binom{34}{0} }{\binom{40}{6}}}$ = 3838380

```{r}
choose(6, 6) * choose(34, 0) / choose(40, 6)
choose(6, 5) * choose(34, 1) / choose(40, 6)
choose(6, 4) * choose(34, 2) / choose(40, 6)
1 / (choose(6, 6) * choose(34, 0) / choose(40, 6))
```
