---
title: "HW10"
author: "Darnell Chen"
date: "2024-12-03"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 10.1.2

a)  Since we want the mean of the two machines to be the same, we thus have $\mu_1 - \mu_2 = 0$. Our two test statistics $\bar{x}_1$ and $\bar{x}_2$ come out to 16.015 and 16.005 respectively. Using these two test statistics, we can find the p-value for our statistical inference:

$$
\begin{aligned}
z_0 &= \frac{(\bar{x}_1 - \bar{x}_2) - \Delta}{\sqrt{\frac{\sigma^2_1}{n_1} + \frac{\sigma^2_2}{n_2}}}\\
&= \frac{16.015-16.005}{\sqrt{\frac{0.02^2}{10}+\frac{0.025^2}{10}}}\\
&\approx 0.9877296
\end{aligned}
$$ We have a two-sided interval since $H_1$ is $\mu \neq \mu_0$. Since $P(Z > 0.9877296) \approx 0.1616425$, this means our p-value is 0.3232851, since we have the consider the lower-tail rejection area too.

Since our p-value is greater than our $\alpha$ of 0.05, we will thus fail to reject our null hypothesis, where our $\mu_0 = \mu$ - and the engineer is thus correct.

b)  Our 95% CI will be double sided, thus we're looking for:

$$
\begin{aligned}
(\bar{x}_1 - \bar{x_2}) \pm z_{\frac{\alpha}{2}}\sqrt{\frac{\sigma^2_1}{n_1} + \frac{\sigma_2^2}{n_2}} &= (16.015-16.005)+z_{0.025}\sqrt{\frac{0.02^2}{10} + \frac{0.025^2}{10}}\\
&\approx 0.01 \pm 1.96(0.0101242)\\
&\approx [-0.009843, ~0.029843]
\end{aligned}
$$

Since 0 is within our CI, we thus fail to reject the null hypothesis, since our interval contains the chance that our mean difference between our two machines is 0 (they have the same net volume).

c)  Again, we're looking at a two-sided interval, however, this time we're looking for the rejection region when the true mean is 0.04, since $power = 1 - \beta$, and the acceptance region here will give us $\beta$:

$$
\begin{aligned}
z &= \frac{\bar{x}_1-\bar{x}_2-\Delta}{\sqrt{\frac{\sigma_1^2}{n_1} + \frac{\sigma_2^2}{n_2}}}\\
&= \frac{16.015 - 16.005 - 0.04}{\sqrt{\frac{0.02^2}{10}+\frac{0.025^2}{10}}}\\
&\approx \frac{0.01 - 0.04}{0.0101242}\\
&\approx -2.963189
\end{aligned}
$$

Our rejection region will be the area less than our z-value and greater than $|z|$, $power = 2 \cdot P(Z < -2.963189) \approx 0.003044698$

```{r}
machine1 <- c(16.03, 16.04, 16.05, 16.05, 16.02, 16.01, 15.96, 15.98, 16.02, 15.99)
machine2 <- c(16.02, 15.97, 15.96, 16.01, 15.99, 16.03, 16.04, 16.02, 16.01, 16.00)

mean(machine1)
mean(machine2)

2*(1-pnorm(0.9877296))

2*pnorm(-2.96318878995)
```

$~$

## 10.2.2

a)  This is a small sample size with equal variance assumption. So we have:

$S_p^2 = \frac{(n_1-1)S_1^2 + (n_2-1)S_2^2}{n_1 + n_2 - 2} = \frac{(15-1)(4) + (15-1)(6.25)}{15+15-2} = 5.125$

This means our estimated standard deviation is $S_p = \sqrt{5.125} \approx 2.263846$. Using this, we can get our $t_0$ for our p-value:

$$
\begin{aligned}
t_0 &= \frac{\bar{x}_1 - \bar{x}_2 - \Delta}{S_p\sqrt{\frac{1}{n_1} + \frac{1}{n_2}}}\\
&= \frac{4.7 - 7.8}{\sqrt{5.125}\sqrt{\frac{1}{15}+ \frac{1}{15}}}\\
&\approx -3.7501219
\end{aligned}
$$ Note that we set delta to 0 since our null hypothesis is $\mu_1 = \mu_2$, so their difference is 0.

Using our t-table, we find that $t_{0.025, 28} = -2.048$. Since our test statistic less less than our critical value, we will thus reject our null hypothesis.

Since this is a two-sided hypothesis, our p-value will be $2 \cdot P(t_{28} < -3.7501219) \approx 0.001$.

Since our p-value is much less than our $\alpha = 0.05$, we will thus reject our null-hypothesis.

$~$

b)  To find our CI, we will use the following formula:

$$
\begin{aligned}
(\bar{x}_1 - \bar{x}_2) \pm t_{\frac{\alpha}{2} = 0.025}S_p\sqrt{\frac{1}{n_1} + \frac{1}{n_2}} &= (4.7 - 7.8)\pm 2.048\sqrt{5.125}\sqrt{\frac{1}{15}+\frac{1}{15}}\\
&\approx -3.02 \pm 1.692958\\
&\approx [-4.792958, -1.4070417]
\end{aligned}
$$

Since 0 is not in our CI, we will thus reject the null hypothesis.

$~$

## 10.2.6

a)  We have a small sample size with unequal variance, thus our degrees of freedom for our critical value will be:

$v = \frac{(\frac{s^2_1}{n_1} + \frac{s^2_2}{n_2})^2}{\frac{(\frac{s^2_1}{n_1})^2}{n_1-1} + \frac{(\frac{s^2_2}{n_2})^2}{n_2-1}} = \frac{(\frac{12^2}{10} + \frac{22^2}{16})^2}{\frac{(\frac{12^2}{10})^2}{10-1} + \frac{(\frac{22^2}{16})^2}{16-1}} \approx 23.72112877 \approx 24$

Thus our critical value is $-t_{0.025, 24} = -1.711$. We then want the test statistic to compare it to:

$$
\begin{aligned}
t_0 &= \frac{(\bar{x}_1-\bar{x}_2) - \Delta}{\sqrt{\frac{s^2_1}{n_1}+\frac{s^2_2}{n_2}}}\\
&= \frac{290-321}{\sqrt{\frac{12^2}{10}+\frac{22^2}{16}}}\\
&\approx -4.639284
\end{aligned}
$$ Since our test statistic is less than our critical value, we will thus reject our null hypothesis.

To prove with our p-value, we know that $P(t_{24} < -4.629284) \approx 0$. Since our p-value is much less than our alpha $\alpha = 0.05$, we thus reject our null hypothesis.

$~$

b)  We're looking at:

$$
\begin{aligned}
t_0 &= \frac{(\bar{x}_1-\bar{x}_2) - \Delta}{\sqrt{\frac{s^2_1}{n_1}+\frac{s^2_2}{n_2}}}\\
&= \frac{290-321 + 25}{\sqrt{\frac{12^2}{10}+\frac{22^2}{16}}}\\
&\approx -0.897926
\end{aligned}
$$ From earlier, we calculated that our critical value is -1.711. Since our observed statistic larger than our critical value, that means it's in the acceptance region. Hence, we fail to reject the null hypothesis here.

$~$

c)  To find the CI, we are computing:

$$
\begin{aligned}
(\bar{x}_1 - \bar{x}_2) \pm t_{24}\sqrt{\frac{s^2_1}{n_1} + \frac{s_2^2}{n_2}} &= (290 - 321)\pm 1.711\sqrt{\frac{12^2}{10}+\frac{22^2}{16}}\\
&\approx -31 \pm 11.433014\\
&\approx [-42.433014, -19.5669858]
\end{aligned}
$$

Our CI shows that supplier 2 has a higher average impact strength, ranging from 19.5669 to 42.433 foot-pounds higher.

$~$

## 10.4.2

a)  Given that the difference in coding time roughly follows our qq-distribution line, we can reasonably assume that the difference in coding time in normally distributed. (WiFi is out so I can't do anderson darling test)

b)  To find our standard deviation $s_D$, we will calculate:

$s_D = \sum_{i=0}^{12} \frac{(x_i-\bar{x} )^2}{n-1} \approx 2.9644$

The average of the differences is $\bar{d} = \frac{2}{3}$. Then for our CI, we calculate:

$$
\begin{aligned}
\bar{d} \pm t_{\frac{\alpha}{2}, ~n-1} \cdot \frac{s_D}{\sqrt{n}} &= \frac{2}{3} \pm 2.201 \cdot \frac{2.9644}{\sqrt{12}}\\
&\approx \frac{2}{3} \pm 1.883525\\
&\approx [-1.21685, 2.55019]
\end{aligned}
$$
Since the CI leans more towards the positive side, this means that design language 1 is more preferable.


```{r}
programmer1 <- c(17, 16, 21, 14, 18, 24, 16, 14, 21, 23, 13, 18)
programmer2 <- c(18, 14, 19, 11, 23, 21, 10, 13, 19, 24, 15, 20)

differences = programmer1 - programmer2

qqnorm(differences)
qqline(differences)

sd(differences)
mean(differences)

t.test(programmer1, programmer2, paired = TRUE)
```


